Manuscript_analyses

### 2022-05-13 Manuscript_analyses.Rmd
update

# THIS LOOKS BAD, BECAUSE OF Low-Milk-high-emissions households. Would be good to break the axis - any ideas?

@@

```{r varkernelslicerange}
slice<-uncertainty::varslice_resample(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                                 out_var = GHG_simulation_scenarios$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = (max(out_var)-min(out_var))/1000)

@@

@@

# THIS WON'T REALLY WORK... peak is too high, everything else becomes invisible

>>>>

# THIS LOOKS BAD, BECAUSE OF Low-Milk-high-emissions households. Would be good to break the axis - any ideas? (I removed the extreme peak now by excluding underperforming dairy households)

@@

```{r varkernelslicerange}
slice<-uncertainty::varslice_resample(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                                 out_var = GHG_simulation_scenarios$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

@@

ggplot(data=slice$slice, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~density~of~milk~production~(XX~CO[2]-eq~kg^-1)))

@@

# THIS WON'T REALLY WORK... peak is too high, everything else becomes invisible (should work now, afte excluding underperforming households)
